---
title: "API : fredr"

description: Access online data through the fredR API.
authors:
  - name: Thierry Warin
    url: https://www.nuance-r.com/principalInvestigator.html
    affiliation: SKEMA Business School (Raleigh, NC)
    affiliation_url: https://www.skema-bs.fr/campus/campus-raleigh 
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_depth : 4
bibliography: virtualCampus.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Database description 

"The Federal Reserve Economic Data (fredR) provides a complete set of R bindings to the Federal Reserve Economic Data (FRED) RESTful API, provided by the Federal Reserve Bank of St. Louis. The functions gives access to all indicators and allow the user to search for and fetch more than 627 000 series from 89 sources as well as associated metadata within the FRED database." 

<!--
Possibilité de faire du web scraping pour aller trouver le nb de series provenant de fredr pour avoir la donnée exacte en temps réel
-->

The Federal Reserve Economic Data : https://fred.stlouisfed.org/

## Necessary key 

To assess FRED data, you need an API key that is provided by the institution. First, you have to (freely) register to the institution at: https://research.stlouisfed.org/useraccount/register/step1. After providing a valid email adress, you will receive an activation email. Click on it, and you will be forwarded to a control panel. 

Click on the Account tab, and select API Keys. Then, click on + Request API Key. After entering details on the use of fredR’s data, you will be provided with a unique API key. Such key will be in the form of:

> APIkey <- "abcdefghijklmnopqrstuvwxyz123456" 

First, you need to enter your API key in the function fredr_set_key(). This will take the API Key given by fredR and will allow the acces to the database. 

```{r, message=FALSE, warning=FALSE, eval=FALSE}
# Register API key
library(fredr)
fredr_set_key("abcdefghijklmnopqrstuvwxyz123456")
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# Register API key
library(fredr)
fredr_set_key("01317e24bbe4b76781ff4ffee4c5a8b9")
#fredr_set_key("01317e24bbe4b76781ff4ffee4c5a8b9")
# Using search function
fredr_series_search_text(search_text = "exchange rate")
```
Now, with your API key and using the fredR library, you can access data sources!

## Functions 

The functions listed below allow you to search and download specific data from the fredR database using a key and different parameters. Each of these functions are detailed below and some examples are provided. 

* **fredr_search()**
* **fredr_observations()**

### fredr_search()

By using the search function fredr_search(), you will have all indicators related to a specific query. The function fredr_search() takes as an input an indicator from the fredR database and returns a table containing information related to the input inserted. 

For example, it could be interesting to evaluate the exchange rate. 

```{r, message=FALSE, warning=FALSE}

# Using search function 
fredr_series_search_text(search_text = "exchange rate") 
```

### fredr_observations()

By using the observation function fredr_observations(), you can add parameters in order to evaluate data concerning an input. 

For example, it could be interesting to evaluate the exchange rate (input) between Euro and $US from 2000 to 2017 (“EXUSEU” in the previous results table).

```{r, message=FALSE, warning=FALSE}

# Downloading data concerning exchange rate
dataFred <- fredr_series_observations(series_id = "EXUSEU", 
             observation_start = as.Date("2000-01-01"),
             observation_end = as.Date("2017-01-01"))
```

## tl;dr

```{r, eval=FALSE, message=FALSE, warning=FALSE}
# Register API key
library(fredr)
fredr_set_key("abcdefghijklmnopqrstuvwxyz123456")

# Using search function 
fredr_series_search_text(search_text = "exchange rate")

# Downloading data concerning exchange rate
dataFred <- fredr_series_observations(series_id = "EXUSEU", 
             observation_start = as.Date("2000-01-01"),
             observation_end = as.Date("2017-01-01"))

```

## Code learned this week

| **Command** | **Detail** |
| ------------------------------ | ----------------------------------  |
| fredr_set_key() | Set the key to allow access to the data |
| fredr_search() | Find data related to an input given |
| fredr_observations() | Find data related to parameters |

## References

This course uses the [fredR package documentation](https://cran.r-project.org/web/packages/fredr/vignettes/fredr.html#retrieve-series-observations) 
