---
title: "API : UNIDO"

description: Access online data through the UNIDO API.
authors:
  - name: Thierry Warin
    url: https://www.nuance-r.com/principalInvestigator.html
    affiliation: SKEMA Business School (Raleigh, NC)
    affiliation_url: https://www.skema-bs.fr/campus/campus-raleigh 
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_depth : 4
bibliography: virtualCampus.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Database description 
The United Nations Industrial Development Organization (UNIDO) provides a variety of databases on business structure and statistics on indicators of industrial performance by country. 

United Nations Industrial Development Organization (UNIDO) data :  https://stat.unido.org/rest/apidoc 



```{r, message=FALSE, warning=FALSE, eval=FALSE}
library(httr)
library(jsonlite)

url <- "https://stat.unido.org/rest/dblist"

get_stuff <- GET(url)

get_stuff

get_stuff_text <- content(get_stuff, "text")

get_stuff_text
```

```{r, message=FALSE, warning=FALSE, eval=FALSE}


get_stuff_json <- fromJSON(get_stuff_text, flatten = TRUE)

get_stuff_df <- as.data.frame(get_stuff_json)

View(get_stuff_df)


```

In order to load the database, you need to add the database name to the URL. The spaces in the name need to be replace by "%20".


```{r, message=FALSE, warning=FALSE, eval=FALSE}


url <- "https://stat.unido.org/rest/dbinfo/CIP%202019"

get_stuff <- GET(url)

get_stuff

get_stuff_text <- content(get_stuff, "text")

get_stuff_json <- fromJSON(get_stuff_text, flatten = TRUE)

get_stuff_json

#get_stuff_df <- as.data.frame(get_stuff_json)

#View(get_stuff_df)

```
```{r, message=FALSE, warning=FALSE, eval=FALSE}


db=CIP 2019&cc=124&variable=02&start=2008&end=2009

```



Now, with your API key and using the fredR library, you can access data sources.

## Functions 

The functions listed below allow you to search and download specific data from the fredR database using a key and different parameters. Each of these functions are detailed below and some examples are provided. 

* **fredr_search()**
* **fredr_observations()**

### fredr_search()

By using the search function fredr_search(), you will have all indicators related to a specific query. The function fredr_search() takes as an input an indicator from the fredR database and returns a table containing information related to the input inserted. 

For example, it could be interesting to evaluate the exchange rate. 

```{r, message=FALSE, warning=FALSE}

# Using search function 
fredr_series_search_text(search_text = "exchange rate") 
```

### fredr_observations()

By using the observation function fredr_observations(), you can add parameters in order to evaluate data concerning an input. 

For example, it could be interesting to evaluate the exchange rate (input) between Euro and $US from 2000 to 2017 (“EXUSEU” in the previous results table).

```{r, message=FALSE, warning=FALSE}

# Downloading data concerning exchange rate
dataFred <- fredr_series_observations(series_id = "EXUSEU", 
             observation_start = as.Date("2000-01-01"),
             observation_end = as.Date("2017-01-01"))
```

## tl;dr

```{r, eval=FALSE, message=FALSE, warning=FALSE}
# Register API key
library(fredr)
fredr_set_key("abcdefghijklmnopqrstuvwxyz123456")

# Using search function 
fredr_series_search_text(search_text = "exchange rate")

# Downloading data concerning exchange rate
dataFred <- fredr_series_observations(series_id = "EXUSEU", 
             observation_start = as.Date("2000-01-01"),
             observation_end = as.Date("2017-01-01"))

```

## Code learned this week

| **Command** | **Detail** |
| ------------------------------ | ----------------------------------  |
| fredr_set_key() | Set the key to allow access to the data |
| fredr_search() | Find data related to an input given |
| fredr_observations() | Find data related to parameters |

## References

This course uses the [fredR package documentation](https://cran.r-project.org/web/packages/fredr/vignettes/fredr.html#retrieve-series-observations) 
