---
title: "API : OECD"

description: |
  Access online data through the OECD API.
authors:
  - name: Thierry Warin
    url: https://www.nuance-r.com/principalInvestigator.html
    affiliation: SKEMA Business School (Raleigh, NC)
    affiliation_url: https://www.skema-bs.fr/campus/campus-raleigh 
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_depth : 4
#bibliography: virtualCampus.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Database description 

The Organisation for Economic Co-operation and Development (OECD) is an intergovernmental economic organisation with 36 member countries. It is a forum of countries providing a platform to compare policy experiences, seek answers to common problems, identify good practices and coordinate domestic and international policies of its members.

OECD : https://www.oecd.org/about/

## Functions

* **search_dataset()**
* **get_data_structure**
* **get_datasets()**

Each of these functions are detailed in this course and some examples are provided. 

### search_dataset()**

The function search_dataset() searches for OECD indicators. It takes as an input the indicator that would be useful for your analysis. It searches and returns a table of all the available indicator related to the input inserted.


```{r}
# Loading OECD library
library(OECD)

# List all available datasets
dataset_list <- get_datasets()

# Search all indicators with the term "unemployment"
search_dataset("unemployment", data = dataset_list)

```

* **get_data_structure**

The function get_data_structure takes as an input the id associate with the dataset and returns the structure of any query made with the OECD package.

```{r}
# Structure of a query
dstruc <- get_data_structure("DUR_D")
str(dstruc, max.level = 1)
```

* **get_datasets()**

The function get_datasets takes as an input the dataset id and filters. Add a variable to list all of the specific filters  allows to simplify the input of the function. get_datasets returns a dataframe containing the selected data.

```{r}
# Filter use to narrow the research (Canada-Germany-France-USA; male and female; 20-24 years old)
filter_list <- list(c("DEU", "FRA", "CAN", "USA"), "MW", "2024")

# Dataframe containing selected data
unemployementOECD <- get_dataset(dataset = "DUR_D", filter = filter_list)
unemployementOECD[1:6,]
```

## tl;dr

```{r}
# Loading OECD library
library(OECD)

# List all available datasets
dataset_list <- get_datasets()

# Search all indicators with the term "unemployment"
search_dataset("unemployment", data = dataset_list)

# Structure of a query
dstruc <- get_data_structure("DUR_D")
str(dstruc, max.level = 1)

# Filter use to narrow the research (Canada-Germany-France-USA; male and female; 20-24 years old)
filter_list <- list(c("DEU", "FRA", "CAN", "USA"), "MW", "2024")

# Dataframe containing selected data
unemployementOECD <- get_dataset(dataset = "DUR_D", filter = filter_list)
unemployementOECD[1:6,]


```

## Code learned this week

| **Command** | **Detail** |
| ------------------------------ | ----------------------------------  |
| search_dataset() | Search for OECD indicators |
| get_data_structure() | Read the structure of any query made with the OECD package |
| get_datasets() | Find data related to the indicators |

Distill is a publication format for scientific and technical writing, native to the web. 

Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.





